\texttt{batman}: BAsic Transit Model cAlculatioN in Python

### 2015-08-04 manuscript/ms.tex
update manuscript in response to referee

Computationally intensive sections of code (including all of the transit model calculation) are written as C extension modules with the Python/C API, which improves the performance by roughly two orders of magnitude over a pure Python implementation.  \texttt{batman} also includes the option to parallelize at the C level with OpenMP, which further speeds up the calculation. The number of processors is specified by the user.  \texttt{batman} will raise an exception if the user attempts to parallelize a calculation on a system where OpenMP is not supported.

>>>>

Computationally intensive sections of code (including all of the transit model calculation) are written as C extension modules with the Python/C API, which improves the performance by \blue{a factor of 30} over a pure Python implementation \blue{for quadratic limb darkening}.  \texttt{batman} also includes the option to parallelize at the C level with OpenMP, which further speeds up the calculation. The number of processors is specified by the user.  \texttt{batman} will raise an exception if the user attempts to parallelize a calculation on a system where OpenMP is not supported.
